What is disputed on the web?

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Making more changes to the WICOW paper requested by reviewers

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 31st 2010, and pages written between January 1st and January 31st of every year from 2000 to 2010. This amounts to approximately 3.6 million strings that our classifier believes are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

@@

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{Adler2008b} identifies potentially unreliable sections of an article by analyzing its edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos. Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing; some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user. These metrics do a good job at detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.

In our research, we are following a third approach. We aim to inform users when information that they encounter is disputed by another source. We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed. For example, if a user is reading a page that says ``Elvis is alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to the corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine whether this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important. One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that Obama is a Muslim'' then that suggests that the contradiction with ``Obama is a Muslim'' is likely to be genuine. 
The corresponding disadvantage would be that if one looks for disputes, one would only detect contradictions that humans have found and believe are important.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5_bigger.pdf}
	\caption{Number of claims containing a particular noun on January 10th of any particular year}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 6.1 million text strings, of which 3.6 million were identified by our classifier as being unambiguous disputable claims. This does not mean that there are 3.6 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.

@@

Our data set currently includes approximately 3.6 million records. In the future we intend to expand this by several orders of magnitude.

>>>>

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 31st 2010, and pages written between January 1st and January 31st of every year from 2000 to 2010. This amounts to approximately 4.2 million strings that our classifier believes are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

@@

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{Adler2008b} identifies potentially unreliable sections of an article by analyzing its edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos. Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing; some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user. These metrics do a good job of detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.

In our research, we are following a third approach. We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed by another source. For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder knows about another page that argues that this claim is false, then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to the corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine whether this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. Kawahara et al~\cite{Kawahara2008} and Statement Map~\cite{Murakami2009} use contradiction detection to inform a user when a set of documents contain claims that appear to contradict each other. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important. One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that Obama is a Muslim'' then that suggests that the contradiction with ``Obama is a Muslim'' is likely to be genuine. 
The corresponding disadvantage would be that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects. To put it another way, Dispute Finder can be thought of as a second order of opinion mining in which we are looking for opinions about opinions.

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5_bigger3_small.pdf}
	\caption{Number of claims containing a particular noun made during January of any particular year}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 7 million text strings, of which 4.2 million were identified by our classifier as being unambiguous disputable claims. This does not mean that there are 4.2 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.

@@

Our data set currently includes approximately 4.2 million records. In the future we intend to expand this by several orders of magnitude.
